Precision calculations of the cosmic shear power spectrum projection

### 2017-02-16 cfhtlens.tex
very minor

\mk{We also find that the cosmological constraints from tomographic KiDS are robust
to the flat-sky and Limber approximations. The case ExtL1FlHyb that was used
for KiDS data in \citep{KiDS-450} and \cite{joudaki/etal:2017} introduces
errors that are more than an order of magnitude lower than the cosmic variance
for that survey, and thus this approximation has negligible effect on
cosmological parameters.}

>>>>

\mk{We also find that the cosmological constraints from tomographic KiDS are robust
to the flat-sky and Limber approximations. The case ExtL1FlHyb that was used
for KiDS data in \citet{KiDS-450} and \cite{joudaki/etal:2017} introduces
errors that are more than an order of magnitude lower than the cosmic variance
for that survey, and thus this approximation has a negligible impact on the
cosmological parameters.}
